On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-02-24 AvdMomZvolA_examples/ips_examples.tex
[AMZAE] Plan for rails
[AMZAE] Remove TODO notes
[AMZAE] Just EOLs
[AMZAE] Drafts for two more sections

@@

\section{Final remarks}
All the given PIPSs were obtained through a combination of computer search an intuition of the authors;

There is still no general construction for a rails or scissors PIPS of given cardinality.
For rails PIPSs, we can conjecture that there exists a set of arbitrary cardinality with 2 points on one line
and all the rest on the other;
on the other hand, we still have not found any rails PIPSs with 4 and 5 points on the lines.

@@

\printbibliography
%\bibliography{literature}

>>>>

Two IPSs below have been obtained by dilating~\cite[Fig. 34]{avdeev2019particular} by $23$ and $29$  resp.;
third one has been constructed by dilation and merge.

@@

\section{Example of sets with many common points that canot be merged}

TODO: three ''romantic'' pictures in a row.

TODO: specify the irrational distance:

Note that distance between the non-adoptable points is
\begin{equation}
	\sqrt{\left(\frac{}{} - \frac{}{}\right)^2 + \left(\frac{}{} - \frac{}{}\right)^2}
\end{equation}

\section{Integral point sets with two axes of symmetry}

TODO:

TODO: 11_14450_1_8693fad981c82dc92d7c9365bcb9945e

The set on Fig. TODO has been obtained from the set on Fig. TODO by dilation by 5.

The set on Fig. TODO has been obtained from the set on Fig. TODO by dilation by 42 (or less? TODO).

\section{Other examples}

TODO: 8_2535_1_d680ff2d172ebe40250a54ca9419af34

\section{Final remarks}
All the given planar integral point sets were obtained through a combination of computer search an intuition of the authors;

@@

\printbibliography
